Query Optimization for Dynamic Imputation

### 2017-05-12 paper/experiments.tex
paper: fix up title capitalization

\subsection{Data sets}\label{subsec:datasets}
We collect three data sets for our experiments.
For all data sets, we selected a subset of the original attributes.
We also transform all data values to an integer representation by enumerating strings and transforming floating-point values into an appropriate range.

@@

\subsubsection{Planning times}
\begin{table}
\centering
\input{tables/planning_summary_exact_pareto.tex}
\caption{Planning times are sub-second for up to 4 joins. For 5+  joins planning times rise. Many practical queries
can be formulated with a smaller number of joins, but to support more complex queries \ProjectName{} provides an
optimization that maintains approximate Pareto sets for queries with many joins. This reduces the 29 second
planning time shown for 7 joins by approximately 45\%, on average.
\todo{update with new table and values}
}
\label{table:planning-times}
\end{table}

@@

However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits our planning algorithm by constructing a series of queries with increasing number of joins.
We used the CDC tables and evaluated a combination of self-joins and joins across reference tables.
Planning times for queries involving 1--5 joins, which is a practical value for real world exploratory queries, take less than a second.
\todo{update: For queries with 7 joins, planning time increases substantially to 29 seconds, on average. We introduced an optimization that reduces
the plan space by maintaining only approximations of the Pareto set for queries involving a large number of joins.
With this optimization, the same set of queries have an average planning time of 16 seconds (2 seconds SE).}

>>>>

\subsection{Data Sets}\label{subsec:datasets}
We collect three data sets for our experiments.
For all data sets, we selected a subset of the original attributes.
We also transform all data values to an integer representation by enumerating strings and transforming floating-point values into an appropriate range.

@@

\subsubsection{Planning Times}
\begin{table}
\centering
\input{tables/planning_summary_exact_pareto.tex}
\caption{Planning times are sub-second for up to 4 joins. For 5+  joins planning times rise. Many practical queries
can be formulated with a smaller number of joins, but to support more complex queries \ProjectName{} provides an
optimization that maintains approximate Pareto sets for queries with many joins. This reduces the 29 second
planning time shown for 7 joins by approximately 45\%, on average.
\todo{update with new table and values}
}
\label{table:planning-times}
\end{table}

@@

However, \ProjectName{}'s planning algorithm is still exponential in the number of joins in the plan, and the use of Pareto sets exacerbates this exponential growth.
We explored the limits our planning algorithm by constructing a series of queries with increasing number of joins.
We used the CDC tables and evaluated increasing number of joins across tables.
Planning times for queries involving 1--5 joins, which is a practical value for real world exploratory queries, take less than a second.
\todo{update: For queries with 7 joins, planning time increases substantially to 29 seconds, on average. We introduced an optimization that reduces
the plan space by maintaining only approximations of the Pareto set for queries involving a large number of joins.
With this optimization, the same set of queries have an average planning time of 16 seconds (2 seconds SE).}
